Data_Analysis_MS_ddm_exp1

### 2018-10-03 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
updae plots

```{r plot_match_RT_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)

@@

```{r plot_match_dprime_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'dprime', inData = df.M1.V.SDT_l)
```

```{r plot_categ_ACC_val_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)

```{r plot_categ_ACC_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)
```

```{r plot_categ_RT_val_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'RT', inData = df.C1.V.sum_rt_acc_l)

```{r plot_categ_RT_Id_data,echo=FALSE,warning=FALSE, message=FALSE}
MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'RT', inData = df.C1.V.sum_rt_acc_l)
```

>>>>

```{r plot_match_data,echo=FALSE,warning=FALSE, message=FALSE}
#MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)
Mplots(saveDir = traDir, curDir = curDir, expName = 'exp7', df.M1.V.SDT_l,df.M1.V.sum_rt_acc_l)

@@

```{r plot_categ_val_data,echo=FALSE,warning=FALSE, message=FALSE}
CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'id', df.C1.V.sum_rt_acc_l)
CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'val', df.C1.V.sum_rt_acc_l)
```

### 2018-10-03 Results/preproc/MS_ddm_preproc.rmd
updae plots

```{r plot_match_data,echo=FALSE,warning=FALSE, message=FALSE}
#plot the rT data from matching task
MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'RT', inData = df.M1.V.sum_rt_acc_l)

# plot the dprime data from matching task
MSplots(saveDir = traDir, curDir = curDir, task = 'match',type = 'dprime', inData = df.M1.V.SDT_l)

@@

```{r plot_categ_val_data,echo=FALSE,warning=FALSE, message=FALSE}
# plot ACC
MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)

# plot RT
MSplots(saveDir = traDir, curDir = curDir, task = 'val',type = 'RT', inData = df.C1.V.sum_rt_acc_l)

```{r plot_categ_ID_data,echo=FALSE,warning=FALSE, message=FALSE}
# plot ACC
MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'ACC', inData = df.C1.V.sum_rt_acc_l)
# plot RT
MSplots(saveDir = traDir, curDir = curDir, task = 'id',type = 'RT', inData = df.C1.V.sum_rt_acc_l)
```

```{r plot_noTask_data,echo=FALSE,warning=FALSE, message=FALSE}
# plot ACC
MSplots(saveDir = traDir, curDir = curDir, task = 'categ',type = 'ACC', inData = df.C1.V.sum_rt_acc_noTask_l)
# plot RT
MSplots(saveDir = traDir, curDir = curDir, task = 'categ',type = 'RT', inData = df.C1.V.sum_rt_acc_noTask_l)
```

>>>>

```{r plot_match_data,echo=FALSE,warning=FALSE, message=FALSE}
Mplots(saveDir = traDir, curDir = curDir, expName = 'exp7', df.M1.V.SDT_l,df.C1.V.sum_rt_acc_l)
```

```{r plot_categ_data,echo=FALSE,warning=FALSE, message=FALSE}
# plot id-based data
CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'id', df.C1.V.sum_rt_acc_l)

# plot val-based data
CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'val', df.C1.V.sum_rt_acc_l)

@@

```{r plot_noTask_data,echo=FALSE,warning=FALSE, message=FALSE}
# plot ACC
CAplots(saveDir = traDir, curDir = curDir,expName = 'exp7', task = 'categ', df.C1.V.sum_rt_acc_noTask_l)
#MSplots(saveDir = traDir, curDir = curDir, task = 'categ',type = 'ACC', inData = df.C1.V.sum_rt_acc_noTask_l)
# plot RT
#MSplots(saveDir = traDir, curDir = curDir, task = 'categ',type = 'RT', inData = df.C1.V.sum_rt_acc_noTask_l)
```
